Software Citation Principles

### 2016-08-21 sc-principles/rebuttal-2/rebuttal.tex

\textbf{Our response:}

\end{itemize}

\item \textbf{Reviewer comment:}
\emph{I am also not convinced by the arguments against hashes as identifiers:}

\textbf{Our response:}
As a general comment, we prefer to recommend DOIs associated with specific,
released versions of software for a number of reasons: not specific to VCS used,
more guaranteed persistence, same persistent identifier used for publications and data.
However, there are certain sitatuions where this may not be possible:
(1) the software developers did not register a DOI or release specific
versions, (2) the version of software used does not match what is available
to cite (perhaps they used the dev/prerelease version), etc. In those cases,
falling back on URL+hash would be an approriate way to cite the software used.

### 2016-08-21 sc-principles/software-citation-principles.tex
a few minor edits, removed notes on general url + hash comment

\begin{enumerate}
\item Version numbers/commit references are not guaranteed to be permanent. Projects can be migrated to new version control systems (e.g., SVN to Git). In addition, it is possible to overwrite/clobber a particular version (e.g., force-pushing in the case of Git).
\item A repository address and version number does not guarantee that the software is available at a particular (resolvable) URL, especially as it is possible for authors to remove their content from e.g. GitHub.
\item A particular version number/commit reference may not represent a ``preferred'' point at which to cite the software from the perspective of the package authors.
\end{enumerate}

We recognize however that there are certain situations where it may not be possible for follow the recommended best-practice.
For example, if (1) the software authors did not register a DOI and/or release a specific version or (2) the version of the
software used does not match what is available to cite. In those cases, falling back on a combination of the repository URL and
version number/commit hash would be an appropriate way to cite the software used.

>>>>

\begin{enumerate}
\item Version numbers/commit references are not guaranteed to be permanent. Projects can be migrated to new version control systems (e.g., SVN to Git). In addition, it is possible to overwrite/clobber a particular version (e.g., force-pushing in the case of Git).
\item A repository address and version number does not guarantee that the software is available at a particular (resolvable) URL, especially as it is possible for authors to remove their content from, e.g., GitHub.
\item A particular version number/commit reference may not represent a ``preferred'' point at which to cite the software from the perspective of the package authors.
\end{enumerate}

We recognize that there are certain situations where it may not be possible for follow the recommended best-practice.
For example, if (1) the software authors did not register a DOI and/or release a specific version, or (2) the version of the
software used does not match what is available to cite.
In those cases, falling back on a combination of the repository URL and
version number/commit hash would be an appropriate way to cite the software used.
